Minimizing post shock forecasting error using disparate information

### 2020-06-07 manuscript/manuscript.tex
some edit at the end of introduction
addition of parametric and non-parametric bootstrap result

\begin{enumerate}
  \item Remark for non-uniqueness of $\mathbf{W}^*$ is added in Section \ref{properties}.
  \item Generalizations are added in Section 6
  \item Data analysis is updated with results of weighted adjustment estimators
  \item Some preliminary setup of the simulation is added in Section 4.
  \item RMSE is changed to MSE.
  \item Abstract is updated
\end{enumerate}

@@

Our proposed model in Section \ref{modelsetup} is a simple model with results in Section \ref{properties} easily generalizing to other more complicated models. First, the model can be extended to AR($p$) for $y_{i,t}$ with an additional component $\alpha_i 1(D_{i,t}=T_i^* + 1)$.  The model for $\alpha_i$ in $\mc{M}_2$ may be generalized to $\alpha_i = \mu_{\alpha} + \delta_i' \mathbf{x}_{i, T_i^*+1} + \cdots + \gamma_i \mathbf{x}_{i, T_i^* -(p+1)} + \tilde{\varepsilon}_{i}$ with some proper simple adjustments for SCM method.

@@

Our bootstrap procedure can be extended to approximate the distribution of shock effect estimators from more general time series. %I AM NOT SURE HOW MUCH OF THE FOLLOWING IS NEEDED: \citet{politis1994stationary} motivated a stationary bootstrap method for strictly stationary and weakly dependent time series $\{X_n \colon n \in \mathbb{N}\}$. This algorithm generates a sequence of blocks of observations $B_{I_1, L_1}, B_{I_2, L_2}, \ldots$, where $B_{i,b}= \{X_i, X_{i+1}, \ldots, X_{i+b-1}\}$\footnote{for $j > N$, $X_{j}$ is defined to be $X_k$, where $k = j \hspace{-.1cm} \mod N$ and $X_0 = X_N$}; and the sampling stops when $N$ observations are reached. Note that the collection of random positions $\{I_n \colon n \in \mathbb{N}\}$ is a sequence of i.i.d. discrete uniform random variables; and the collection of random lengths $\{L_n \colon n \in \mathbb{N}\}$ is a sequence of  i.i.d. geometric random variables with parameter $p$. However, the consistency needs to be proved by a case-by-case analysis \citep[Page 66]{politis1999subsampling}. Additionally, the asymptotic accuracy of this algorithm can be sensitive to the selection of $p$. This issue is similar to that of the selection of block size in moving-block bootstrapping \citep{kunsch1989jackknife, liu1992moving}.  More work related to bootstrapping time series  can be referred to Chapters 3 and 4 in \citet{politis1999subsampling}, and \citet{berkowitz2000recent}. It is up to the user in selecting which procedure to choose but under different assumptions on the time-series.

For the use of our methodologies, caution should be dedicated to the construction of donor pool. Otherwise, the result will not be robust to the noises introduced by the unsimilar ones.

>>>>

\begin{enumerate}
  \item Remark for non-uniqueness of $\mathbf{W}^*$ is added in Section \ref{properties}.
  \item Generalizations are added in Section 6
  \item Data analysis is updated with results of weighted adjustment estimators
  \item Some preliminary setup of the simulation is added in Section 4.
  \item RMSE is changed to MSE.
  \item Abstract is updated
  \item Edit the end of the introduction
\end{enumerate}

@@

Our proposed model in Section \ref{modelsetup} is a simple model with results in Section \ref{properties} easily generalizing to other more complicated models.

First, the model can be extended to AR($p$) for $y_{i,t}$ with an additional component $\alpha_i 1(D_{i,t}=T_i^* + 1)$.  The model for $\alpha_i$ in $\mc{M}_2$ may be generalized to $\alpha_i = \mu_{\alpha} + \delta_i' \mathbf{x}_{i, T_i^*+1} + \cdots + \gamma_i \mathbf{x}_{i, T_i^* -(p+1)} + \tilde{\varepsilon}_{i}$ with some proper simple adjustments for SCM method.

@@

Sixth, our bootstrap procedure can be extended to approximate the distribution of shock effect estimators from more general time series. The pseudo-time series generated by parametric bootstrap is not stationary. Note that \citet{politis1994stationary} motivated a stationary bootstrap method for strictly stationary and weakly dependent time series $\{X_n \colon n \in \mathbb{N}\}$. This algorithm generates a sequence of blocks of observations $B_{I_1, L_1}, B_{I_2, L_2}, \ldots$\footnote{The collection of random positions $\{I_n \colon n \in \mathbb{N}\}$ is a sequence of i.i.d. discrete uniform random variables; and the collection of random lengths $\{L_n \colon n \in \mathbb{N}\}$ is a sequence of  i.i.d. geometric random variables with parameter $p$.}, where $B_{i,b}= \{X_i, X_{i+1}, \ldots, X_{i+b-1}\}$\footnote{For $j > N$, $X_{j}$ is defined to be $X_k$, where $k = j \hspace{-.1cm} \mod N$ and $X_0 = X_N$.}; and the sampling stops when $N$ observations are reached.  However, the consistency needs to be proved by a case-by-case analysis \citep[Page 66]{politis1999subsampling}. Additionally, the asymptotic accuracy of this algorithm can be sensitive to the selection of $p$. This issue is similar to that of the selection of block size in moving-block bootstrapping \citep{kunsch1989jackknife, liu1992moving}.  More work related to bootstrapping time series  can be referred to Chapters 3 and 4 in \citet{politis1999subsampling}, and \citet{berkowitz2000recent}. It is up to the user in selecting which procedure to choose but under different assumptions on the time-series.

For the use of our methodology, caution should be dedicated to the construction of donor pool. Otherwise, the result will not be robust to the noises introduced by the the ones that are not similar to the time series of interest.
